%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.5in,top=0.35in,right=0.5in,bottom=0.35in]{geometry} % Document margins
\name{\href{http://zhujiaqi.me}{Jiaqi(Jackie) Zhu}} % Your name
\address{Tampa, FL, 33607 \\ \href{mailto:zhujiaqi@oufl.edu}{zhujiaqi@ufl.edu} \\ (352)-222-7518} 
\begin{document}
%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
%\begin{rSectionNL}{Objective}
%Seeking a full-time position as a Data Analyst or Entry Level Developer where I may
%use my engineering background and my interpersonal skills to further company growth and 
%develop professionally.
%\end{rSectionNL}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSectionNL}{Education}
\begin{rNL}{\rm \textbf{Master of Science in Industrial and Systems Engineering}}{May 2014}{
\rm \textbf{Minor in Computer Engineering} \\ 
\textit{University of Florida, Gainesville, FL} \\ 
GPA: 3.89/4.00 \\
Related Courses: Database Management System, Analysis of Algorithms, Advanced Data Structure, Supply Chain Management, Manufacturing Management, Operations Research, Applied Probability Methods.
}{}
\end{rNL}
 \begin{rNL}{\rm \textbf{Bachelor of Engineering in Ocean and Naval Engineering}}{June 2012}{
 \rm \textit{Tianjin University, Tianjin, China} \\ 
 GPA: 3.31/4.00
 %Related Courses: Operation Research, Logistics Engineering and Management, International Shipping Management, Maritime Business Law
 }{}
 \end{rNL}
\end{rSectionNL}
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}
\begin{rSubsection}{Application Engineer in Elutions}{September 2014 -- Present}{}{}
\item Analyze electricity and gas consumption data from Morrisons and help them with energy saving.
\item Manipulate data for over 500 sites and run regression model with Excel VBA scripts.
\end{rSubsection}
\begin{rSubsection}{Intern in Phenetics.com}{May 2014 -- August 2014}{}{}
\item Intern in a start-up to help the company with algorithm design and Java development.
\item Get first hand experience on technologies like J2EE, Java Database Integration with JDBC,
XML parsing with JDOM and so on.
\end{rSubsection}
\begin{rSubsection}{APLL-ZHIQIN Technology Logistics}{July 2011 -- August 2011}{}{}
\item Collected and analyzed data in delivery order.
\item Monitored the transportation performance and calculated key performance indicator (KPI).
%\item Assisted the senior supervisor of Transportation Dept in routine duties. 
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
\begin{rSubsection}{\href{https://play.google.com/store/apps/details?id=me.zhujiaqi.leetcode&hl=en}{Android Application LeetCode Cracker}}{July 2014 -- August 2014}{}{}
\item Developed a simple Android App to deliver my solutions for coding interview problems on \href{https://leetcode.com/}{LeetCode}.
\item Read my GitHub repository instantly and display information in the App with GitHub Java API.
\item Already got more than 1000 downloads on Google Play.
\end{rSubsection}
%------------------------------------------
\begin{rSubsection}{\href{https://github.com/anuragsoni/AskAlbert}{Build a Website with Database Supported}}{January 2014 -- April 2014}{}{}
\item Built a StackExchange like forum for using by the university students, as part of a course on 
database.
\item Designed the UI and implemented the front-end by utilizing HTML/CSS, JavaScript
\item Designed the ER-model and database schema, utilized Oracle SQL and PHP to support the functionality 
\end{rSubsection}
%------------------------------------------------
%\begin{rSubsection}{\href{https://github.com/zhujiaqi517/FibonacciHeap_ADS}{Implement Dijkstra Algorithm with Fibonacci Heap}}{March 2014}{}{}
%\item Implemented Dijkstra algorithm in Java, using a simple data structure as well as Fibonacci heap.
%\item Developed the Fibonacci heap class, and compared the performance of F-Heap scheme to the simple scheme.
%\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{\href{https://drive.google.com/folderview?id=0B72jE2yMNz2wdU9VanNpZUFXS3M&usp=sharing}{Multi-Criteria Decision Support System Based on VBA}}{September 2013 -- December 2013}{}{}
\item Designed a decision support system to evaluate projects for energy companies.
\item Enabled different type of users to execute their respective functions. Ensured the security of the system, hid data among users and hid the VBA codes.
\item Provided flexibility of the system in changing the number of users, evaluation criteria and its weight.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{\href{https://code.google.com/p/plp-project-zhujiaqi/}{Programming Language Designing and Implementation}}{September 2013 -- December 2013}{}{}
\item Designed and implemented a small sequential programming language, which can manipulate images.
\item The compiler was written in Java, it utilized \href{http://asm.ow2.org/}{ASM framework} to dynamically generate Java bytecode.
\item The compiler scan and parse the source code and generate code for Java Virtual Machine (JVM), with syntax checking and static type checking.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{\href{https://drive.google.com/folderview?id=0B72jE2yMNz2wQXUzZXlWamJjd0E&usp=sharing}{Case Study of Amazon.com's European Distribution Strategy}}{January 2013 -- May 2013}{}{}
\item Analyzed how Amazon made decisions about the expansion to Europe and built their European Distribution Network (EDN).
\item Compared decentralized DCs to centralized DCs, considered sharing inventory strategy when use decentralized DCs.
\item Analyzed other issues Amazon had to face when building EDN, such as DCs location, selling regulations, procurement strategy, volume discount and so on.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{\href{https://drive.google.com/folderview?id=0B72jE2yMNz2wb0xNZl9WeUN1OWs&usp=sharing}{Simulation Study of Jacksonville Container Terminal of Crowley Maritime}}{August 2012 -- December 2012}{}{}
\item Collected data of terminal operations and layout, fitted data to stochastic distributions.
\item Simulated and animated the current unload and load processes in ARENA.
\item Ran scenarios which could potentially improve performance of the system and gave suggestions to the company.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Storage Space Allocation for Containers in Container Yards}{Febuary 2012 -- June 2012}{}{}
\item Designed a Genetic Algorithm for storage space allocation questions in container yard.
\item Derived a good stacking strategy for containers to reduce extra moves. 
\item Implemented and Visualized the algorithm in Matlab.
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSectionNL}{AWARDS \& CERTIFICATIONS}
Six Sigma Green Belt, Institute of Industrial Engineers \hfill January 2014 -- Present \\
FE Industrial, NCEES \hfill May 2014 -- Present 

Achievement Award for New Graduate Students, University of Florida \hfill August 2012 \\
First Prize, Contemporary Undergraduate Mathematical Contest in Modeling, CSIAM \hfill October 2011 \\
\href{https://docs.google.com/file/d/0B72jE2yMNz2wQ1YxYUd4cjJxdGM/edit?usp=sharings}{Honorable Mention, The Mathematical Contest in Modeling}, COMAP \hfill April 2011
\end{rSectionNL}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Chinese Mandarin, English \\
Software \& Tools & Eclipse, Git/GitHub, Arena, SPSS, Minitab, \LaTeX, LINGO, AutoCAD, CPlex  \\
Programming & Java, Bash, R, C/C++, Python, Matlab, VBA \\
Web \& Database & HTML/CSS, JavaScript, PHP, SQL/MySQL \\
%Operation System & Windows, Mac OS X, Unix/Linux
\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------
\end{document}
